Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT

### 2012-08-07 talk/vmil2012/paper.tex
todo
(cfbolz, bivab) abstract

\begin{abstract}
\todo{write}
In pellentesque faucibus vestibulum. Nulla at nulla justo, eget luctus tortor.
Nulla facilisi. Duis aliquet egestas purus in blandit. Curabitur vulputate,
ligula lacinia scelerisque tempor, lacus lacus ornare ante, ac egestas est urna
sit amet arcu. Class aptent taciti sociosqu ad litora torquent per conubia
nostra, per inceptos himenaeos. Sed molestie augue sit amet leo consequat
posuere. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices
posuere cubilia Curae; Proin vel ante a orci tempus eleifend ut et magna. Lorem
ipsum dolor sit amet, consectetur adipiscing elit. Vivamus luctus urna sed urna
ultricies ac tempor dui sagittis. In.
\end{abstract}

@@

>>>>

\begin{abstract}
Guards operations occur frequently in traces generated by tracing just-in-time
(JIT) compilers. Therefore it is important to design and implement them
carefully to find the right trade-off between execution speed, deoptimization,
and memory overhead.  In this paper we describe the design decisions about
guards taken in the implementation of the RPython tracing JIT. Furthermore we
measure various properties of guards.
% \o/
\end{abstract}

@@

\todo{explain example}
%___________________________________________________________________________
